
```{r}
library(tidyverse)

library(fitdistrplus)
source("functions.r")
```

Read the data

```{r}
data_5130 <-  read.csv("../Data/processed data/data_5130.csv")

```

Calculate simple shanon index
```{r}
data_5130 <- simple_shanon_index(data_5130)
```


Get a yes (1) no (0) value if there is detected a enebærbuske.
```{r}
data_5130$enebær <- ifelse(rowSums(data_5130[, grep(paste(c(find_art_nr("Juniperus", latin =  TRUE)[,1]), collapse="|"), names(data_5130))]) > 0,1,0)
```


```{r}
find_art_nr("Juniperus", latin =  TRUE)
```

diversitet:



Get the data ready in the form of two data frames, one with cover data and one with frekvens data.
```{r}
data_5130_site <- data_5130[, c("plot", "site", "year")]

cover_data1 <-  data_5130[, grep("Cover", names(data_5130))]
colnames(cover_data1) <- gsub("Cover", "", colnames(cover_data1))

frekvens_data1 <-  data_5130[, grep("Frekvens", names(data_5130))]
colnames(frekvens_data1) <- gsub("Frekvens", "", colnames(frekvens_data1))
```


```{r}
cover_data <-  cbind(data_5130_site , cover_data1)
frekvens_data <- cbind(data_5130_site, frekvens_data1)
```


Use shanon index v1 to find the shanon index
```{r}
data_5130$shanon_index_v1 <-  shanon_index_v1(cover_data1, frekvens_data1)
```

Sammenligner den naive metode med beta binomial metode.

```{r}
naive_site <-  naive_model(cover_data, frekvens_data, 0.67)

data_5130_lim <- data_5130[,c("site", "year", "simple_shanon_index", "longtitude_mean_site", "latitude_mean_site", "shanon_index_v1")]

data_5130_site_ag <- aggregate.data.frame(data_5130_lim, by = list(data_5130$site), FUN = mean)

data_5130_site_ag <- merge(data_5130_site_ag, naive_site)

data_5130_site_ag$diff <- data_5130_site_ag$shanon_index_v1 - data_5130_site_ag$`Shannon index`

mean(data_5130_site_ag$diff)
```

Jeg får værdien man skal give ved den naive metode hvis man i gennemsnit skal få de værider 0.67, dvs ret højt.






Test something


```{r}
# input is cover data and frekvens data as two data frames, where the rows match for the same observation, and the names of the species match.
shanon_index_v1_beta_data <- function(cover_data, frekvens_data) {
  
  #Load functions 
  library(tidyverse)
  library(fitdistrplus)
  
  #create data frame to hold the fitted values for each species
  beta_fit <- data.frame(matrix(ncol = 3, nrow = 0))
  x <- c("species","a", "b")
  colnames(beta_fit) <- x
  
  # for Each species calculate the shape parameter for the fitted beta distribution and save them in a data frame.
  for (specie in colnames(cover_data)) {
    beta_data <- cover_data[,specie]/16
    beta_data <- beta_data[!(beta_data == 0)]
    
    beta_data <-  ifelse(beta_data == 1, 0.9999, beta_data)
    
    if (length(unique( beta_data)) > 1) {
      beta_data_fitted <- fitdist(beta_data, "beta")
      beta_fit[nrow(beta_fit) + 1,] <- c(specie, beta_data_fitted$estimate[1], beta_data_fitted$estimate[2])
      
    }
  }
  
  # for each plot create a list with all the cover data and a total of how may obersevations.
  shanon_list <- c()
  
  for (row in 1:nrow(cover_data)) {
    total_cover_obs <- sum(cover_data[row,]) #is not currently used
    # Create a list with all the Cover data greater than 0 for a given row
    all_obs <- cover_data[row,] 
    all_obs <- all_obs[all_obs > 0]/16
    obs
    # for a given row, find out what species is found in frekvens
    species_spotted_in_frekvens <- colnames(frekvens_data[c(frekvens_data[row,]  == 1)])
    
    #For each species spotten in frekvens but not in cover, appends its posterior cover to the cover data for that row
    for (species_spotted in species_spotted_in_frekvens ) {
      if (length(cover_data[[species_spotted]][row]) == 1 && cover_data[[species_spotted]][row] == 0) {
        
        all_obs <- append(all_obs, (as.numeric(beta_fit[beta_fit$species == species_spotted,]$a) + 1 -1)/
                            (as.numeric(beta_fit[beta_fit$species == species_spotted,]$a) +
                               as.numeric(beta_fit[beta_fit$species == species_spotted,]$b) + 17 -2))
        
        total_cover_obs <- total_cover_obs +1
      }
      
      
    }
    
    #Calculate the shanon index value and append it to the list
    total_cover <- sum(all_obs)
    shanon_value <- -sum(all_obs/total_cover * log((all_obs/total_cover)))
    
    shanon_list <- append(shanon_list,shanon_value)  
    
  }
  return(beta_fit)
}
```


```{r}
beta_data$mode <- as.numeric(beta_data$a)/(as.numeric(beta_data$a) + as.numeric(beta_data$b) +15)
```

```{r}
beta_data <-  shanon_index_v1_beta_data(cover_data1, frekvens_data1)
mean(beta_data$mode)*16
```


Save the changes

```{r}
write.csv(data_5130, file = "../Data/Processed data//data_5130.csv", row.names=FALSE)
```


