---
title: "Dataprojekt"
author: "Ditte, Malthe & Nikolaj"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)


library(fitdistrplus)
library(tidyverse)
 library(ggmap)
  library(ggplot2)
  library(gifski)
library(png)
library(gganimate)
```

The plant diversity is often calculated by using the number of times a plant in a certain area is observed, without taking into account the knowledge we have about which plants are in the area. 
<br>
Since some plants may be in the area, but is not observed, we loose a lot of valuable information by using this course of action. <br>
To solve this issue the method of pin-point data has been introduced. 
The pin-point data consists of two different forms of datasets. One is a cover-dataset, which contains information from a given plot, about how many times a specie was hit by a pin out of n possible. The other is a frequency-dataset which contains information about whether or not a specie is to be found in the given plot indicated by a binary value (1 for found and 0 for not found). <br>
By using a bayesian method it is possible to use the information from both the cover-dataset and the information from the frequency-dataset.
<br><br>
To model the number of times a specie is hit by a pin we use the binomial model:
$$
P(Y = y| \theta) = {n \choose y}\theta^y(1-\theta)^{n-y}
$$
where $n$ is the total number of pins and $y$ is the number of times the specie is hit by a pin. <br>
The binomial model is used as a likelihood function when modeling the posterior that is used for calculating the Shannon Index in a given plot. 
<br>
We can create a prior $\theta$ for each specie by using both cover and frequency data. The beta model is a conjugacy prior for the binomial model and, thus, is ideal to use. The beta-model is given by 
$$
f(\theta) = \frac{\Gamma (\alpha+\beta)}{\Gamma (\alpha) \Gamma(\beta)}\theta^{\alpha -1}(1-\theta)^{\beta-1}
$$
For each specie we fit a beta-prior using all the cover data where the corresponding frequency data is 1.
<br><br>
Using the above we can form a posterior, that will be an updated beta distribution for each specie in each plot
$$
\theta | (Y = y) \sim Beta(\alpha + y, \beta + n-y)
$$
When the posterior distribution is found for a specie in a given plot, we use the mean posterior as a measure of the abundance for the specie in the plot. <br>

The mean posterior for a Beta-distribution is given by:

$$\frac{\alpha + y}{\alpha + y+\beta + n-y}$$




We work with data only including the terhabtype = 5130 from the NOVANA dataset.
```{r}
cover <- read.csv("cover_data_5130.csv")

freq <- read.csv("frekvens_data_5130.csv")

abiotisk <- read.csv("abiotiske_data_5130.csv")
```

Cover data
```{r}
head(cover[,1:18])
```

In this cover data the number of inserted pins is 16. Thus, n = 16 in our beta-binomial model.
<br>
<br>
Frequency data
```{r}
head(freq[,1:18])
```


Remove "site", "plot", "year"
```{r}
cover_data <- cover[,4:ncol(cover)]
freq_data <- freq[,4:ncol(freq)]
```


Function:
```{r}
shanon_index_v2 <- function(cover_data, freq_data) {
  
  
  
  #create data frame to hold the fitted values for each species
  beta_fit <- data.frame(matrix(ncol = 3, nrow = 0))
 
  x <- c("species","a", "b")
  colnames(beta_fit) <- x
  
  # for Each species calculate the shape parameter for the fitted beta distribution and save them in a data frame.
  for (specie in colnames(cover_data)) {
    beta_data <- cover_data[,specie]/16
    
    #remove all plots with 0 in frekvens.
    beta_data <- beta_data[freq_data[[specie]] == 1]
    
    
    if (length(unique(beta_data)) > 1) {
      beta_data_fitted <- fitdist(beta_data, "beta", method = "mme")
      beta_fit[nrow(beta_fit) + 1,] <- c(specie, beta_data_fitted$estimate[1], beta_data_fitted$estimate[2])
      
    }
  }
  
  # create list for shannon index for each plot
  shanon_list <- c()
  
  for (row in 1:nrow(cover_data)) {
    
    # Create an empty list for a given row
    mean_posterior <- c()

    
    # for a given row, find out what species is found in frekvens
    species_spotted_in_frekvens <- colnames(freq_data[c(freq_data[row,]  == 1)])
    
    #For each species spotten in frekvens, appends its posterior cover to the cover data for that row
    for (species_spotted in species_spotted_in_frekvens ) {
      
        
        alpha_post <- as.numeric((as.numeric(beta_fit[beta_fit$species == species_spotted,]$a) +
                                    as.numeric(cover_data[[species_spotted]][row]) ))
        beta_post <-  as.numeric(beta_fit[beta_fit$species == species_spotted,]$b) + 16 - as.numeric(cover_data[[species_spotted]][row])
        
        mean_posterior <- append(mean_posterior, (alpha_post)/(alpha_post+beta_post))
        
        
      
      
    }
    
    #Calculate the shanon index value and append it to the list after normalizing and removing zeroes

    total_cover <- sum(mean_posterior)
    mean_posterior <- mean_posterior[!(mean_posterior == 0)]
    shanon_value <- -sum(mean_posterior/total_cover * log((mean_posterior/total_cover)))
    
    shanon_list <- append(shanon_list,shanon_value)  
    
  }
  return(shanon_list)
}
```



```{r}
result <- shanon_index_v2(cover_data, freq_data)
```

```{r}
result
```

```{r}
abiotisk$shanon_index <- result 
```



<h3> Animation </h3>

Animation of shanon indexes in plots in Denmark


Converting coordinates from UTM data to latitude longitude.

The function adds two new columns to the dataframe named "latitude" and "longtitude".

```{r}
convert_to_longlat <- function(data_frame_input, UTMx, UTMy, projection = "+proj=utm +zone=32 +ellps=intl +units=m +no_defs +datum=WGS84") {
  #Load Libraries
  library(sp)
  
  # Create a new data frame with only the UTM data
  df <- data.frame(UTMx, UTMy)
  # turn na to 0 for calculations and save which points are na
  df_na <- df
  df[is.na(df)] <- 0
  
  
  #Make it a SP object and specify the projection
  coordinates(df) <-  ~ UTMx + UTMy
  proj4string(df) <- CRS(projection)
  
  #Transform the data to long lat
  df1 <- spTransform(df, CRS("+init=epsg:4326"))
  
  # Write the long lat
  data_frame_input$latitude <-  df1@coords[,2]
  data_frame_input$longtitude <-  df1@coords[,1]
  
  # Turn na back to na
  data_frame_input$latitude[is.na(df_na[1]) ] <- NA 
  data_frame_input$longtitude[is.na(df_na[2]) ] <- NA 
  
  return(data_frame_input)
}
```



```{r}
abiotisk <- convert_to_longlat(abiotisk, abiotisk$UTMx, abiotisk$UTMy)
```


The function animation_map uses longitude and latitude to create an animation of Denmark.
Index is the values displayed as different colours on the map, and time is the column containing the the year the data is from.

```{r}
animation_map <- function(data_frame_in, longtitude, latitude, index, time, duration_time = 15) {
  
  
  #Load map of Denmark
  world.map <- map_data ("world")
  map1 <- world.map %>% filter(region == "Denmark")
  
  # change input values to strings, so it is easier to use.
  index <- deparse(substitute(index))
  time <- deparse(substitute(time))
  latitude <- deparse(substitute(latitude))
  longtitude <- deparse(substitute(longtitude))
  
  # plot the map
  map_ani <-  ggplot(map1)+ 
    geom_map(map = map1, aes(long, lat, map_id = region), fill="white", colour = "black") +
    coord_map()
  
  
  # Add points
  map_ani <-  map_ani +
    geom_point(data = data_frame_in, aes(y= .data[[latitude]], x = .data[[longtitude]], colour = .data[[index]]), alpha = .9, size =10) + 
    
    scale_color_gradientn(colours = rainbow(5)) +
    transition_states(factor(data_frame_in[[time]]), transition_length = 1, state_length = 1) +
    labs(title = "Year: {next_state}") +
    theme_void(base_size = 35)
  
  #create animation
  animate(map_ani,  nframes = 2*length(unique(data_frame_in[[time]])), duration = duration_time, width = 600, height = 400, res = 35)
  
}
```


```{r, warning = FALSE}
animation_map(abiotisk, longtitude, latitude, shanon_index, year)
```











